A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-19 paper/paper.tex
Removed a small amount of unnecessary stuff from the detailed description of McSplit

The remainder of the procedure performs the search.  A label class
$\langle \setG, \setH \rangle$ is selected from $\AlgVar{future}$, where $\setG
\subseteq V(\graphG)$ and $\setH \subseteq V(\graphH)$, using some heuristic
(\lineref{SelectClass}), and from this label class, a vertex $v$ is selected
from $\setG$ (\lineref{SelectVertex}). We now iterate over all
vertices $w$ in $\setH$, exploring the consequences of adding $(v,w)$ to $M$
(\linerangeref{WLoop}{ShrinkM}).  A new set of label-classes,
$\AlgVar{future'}$,
is created (\lineref{NewFuture}); this will be the labelling that results
from adding $(v,w)$ to our mapping.  Every label-class in $\AlgVar{future}$ can
now be split (\linerangeref{InnerLoop}{InnerLoopEnd}) into two new classes. The
first of these classes (\linerangeref{NewPWithEdge}{AddToFutureWithEdge})
contains vertices in $\setG$ adjacent to $v$ and vertices in $\setH$ adjacent to $w$.
This is added to $\AlgVar{future'}$ if both sets contain at least one vertex.
This is then repeated symmetrically for non-adjacency
(\linerangeref{NewPWithoutEdge}{InnerLoopEnd}). A recursive call is then made
(\lineref{ExpandWithV}), on return from which we remove the mapping $(v,w)$.
Having explored all possible mappings of $v$ with vertices in $\setH$ we now
consider what happens if $v$ is not matched
(\linerangeref{RemoveV}{ExpandWithoutV}).

>>>>

The remainder of the procedure performs the search.  A label class
$\langle \setG, \setH \rangle$ is selected from $\AlgVar{future}$
using some heuristic
(\lineref{SelectClass}); from this label class, a vertex $v$ is selected
from $\setG$ (\lineref{SelectVertex}). We now iterate over all
vertices $w$ in $\setH$, exploring the consequences of adding $(v,w)$ to $M$
(\linerangeref{WLoop}{ShrinkM}).  A new set of label-classes,
$\AlgVar{future'}$,
is created (\lineref{NewFuture}); this will be the labelling that results
from adding $(v,w)$ to our mapping.  Every label-class in $\AlgVar{future}$ can
now be split (\linerangeref{InnerLoop}{InnerLoopEnd}) into two new classes. The
first of these classes (\linerangeref{NewPWithEdge}{AddToFutureWithEdge})
contains vertices in $\setG$ adjacent to $v$ and vertices in $\setH$ adjacent to $w$.
This is added to $\AlgVar{future'}$ if both sets contain at least one vertex.
This is then repeated symmetrically for non-adjacency
(\linerangeref{NewPWithoutEdge}{InnerLoopEnd}). A recursive call is made
(\lineref{ExpandWithV}), on return from which we remove the mapping $(v,w)$.
Having explored all possible mappings of $v$ with vertices in $\setH$ we now
consider what happens if $v$ is not matched
(\linerangeref{RemoveV}{ExpandWithoutV}).
